Polyglots: Crossing Origins by Crossing Formats

### 2013-05-09 main.tex
at 10 pages

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Polyglots : Crossing Origins by Crossing Formats}

@@

@@

The existing defense mechanisms fall short to prevent these attacks
from achieving cross-domain communication. 
On the server side, santization is specific to the target language of
the web application. Sanitizing unexpected formats is typically not considered.
On the client side, CSP
has no effect unless the content is interpreted as HTML. This opens up
opportunities for attacks that are based on other formats.

@@

\paragraph{Evaluation and mitigation}
We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites.
%
Unfortunately, several major web sites do not protect against polyglot
attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injec
attacks. In addition,
we have found two major
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.

@@

\subsection{Alexa top 100}
We have conducted two
studies to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 web sites. Because of their dominance 
on the web, these web sites are also the most exposed to security threats.
The first study covers PDF-based polyglot attacks using syntax injection as the 
infiltration method; the second covers content smuggling.
%It does not involve polyglot attacks based on content smuggling, as 
%potential targets generally require authentication before submitting content.
We refrain from mentioning names of individual web sites to prevent exploitation 
before the issues have been properly dealt with. Neither do we disclose 
these web sites as particularly vulnerable. We are in contact with the teams responsible for the web sites to help
mitigate the vulnerabilities.

@@

These recommendations comes with a caveat that need to be taken into consideration. Some user supplied 
content is only meant to be accessible to certain authenticated users, e.g. photos that 
is only shared with friends. In that case, the service needs to transfer the 
credentials required to authenticate the user from the sensitive origin to the sandboxed 
origin, without actually revealing the credentials used in the sensitive origin. 
Revealing the credentials, e.g. using the same cookies on both origins, defeats 
the purpose of the sandbox origin entirely. Currently there is no uniform solution 
to this problem. Some common solutions are encountered: using the hashed 
credentials of the sensitive origin; or generating public, but obscured, links 
that are later shared manually.

@@

We also plan to extend the empirical study to popular services like
HotCRP, Europass CV, and arXiv.org that allow uploading PDF
documents. Authorization is pending for an in-depth security study of
a major conference management system.

>>>>

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{Polyglots: Crossing Origins by Crossing Formats}

@@

\makeatletter
\def\@maketitle{\newpage
 \null
 \setbox\@acmtitlebox\vbox{%
\baselineskip 20pt
%\vskip 2em                   % Vertical space above title.
%\vskip 0em                   % Vertical space above title.
   \begin{center}
    {\ttlfnt \@title\par}       % Title set in 18pt Helvetica (Arial) bold size.
%    \vskip 1.5em                % Vertical space after title.
%This should be the subtitle.
{\subttlfnt \the\subtitletext\par}\vskip 1.25em%\fi
    {\baselineskip 16pt\aufnt   % each author set in \12 pt Arial, in a
     \lineskip .5em             % tabular environment
     \begin{tabular}[t]{c}\@author
     \end{tabular}\par}
 %   \vskip 1.5em               % Vertical space after author.
   \end{center}}
 \dimen0=\ht\@acmtitlebox
% \advance\dimen0 by -12.75pc\relax % comment by Marco Daniel
 \unvbox\@acmtitlebox
 \ifdim\dimen0<0.0pt\relax\vskip-\dimen0\fi}
\makeatother

@@

The existing defense mechanisms fall short to prevent these attacks
from achieving cross-domain communication. 
On the server side, sanitization is specific to the target language of
the web application. Sanitizing unexpected formats is typically not considered.
On the client side, CSP
has no effect unless the content is interpreted as HTML. This opens up
opportunities for attacks that are based on other formats.

@@

\paragraph{Evaluation and mitigation}
We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites.
%
Unfortunately, several major web sites do not protect against polyglot
attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injection
attacks. In addition,
we have found two major
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.

@@

\subsection{Alexa top 100}
We have conducted two
studies to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 web sites. Because of their dominance 
on the web, these web sites are also the most exposed to security threats.
The first study covers PDF-based polyglot attacks using syntax injection as the 
infiltration method; the second covers content smuggling.
%It does not involve polyglot attacks based on content smuggling, as 
%potential targets generally require authentication before submitting content.
We refrain from mentioning names of individual web sites to prevent exploitation 
before the issues have been properly dealt with.
We are in contact with the maintainers of the web sites to help
mitigate the vulnerabilities.

@@

These recommendations come with a caveat to be taken into consideration. Some user supplied 
content is only meant to be accessible to certain authenticated users, e.g. photos that 
is only shared with friends. In that case, the service needs to transfer the 
credentials required to authenticate the user from the sensitive origin to the sandboxed 
origin, without actually revealing the credentials used in the sensitive origin. 
Revealing the credentials, e.g. using the same cookies on both origins, defeats 
the purpose of the sandbox origin entirely. Currently there is no uniform solution 
to this problem. Some common solutions are encountered: using the hashed 
credentials of the sensitive origin; or generating public, but obscured, links 
that are later shared manually.

@@

% We also plan to extend the empirical study to popular services like
% HotCRP, Europass CV, and arXiv.org that allow uploading PDF
% documents. Authorization is pending for an in-depth security study of
% a major conference management system.
